Supplementary Materials

### 2019-01-15 sup_mat/sup_mat.Rmd
Tidied
Should be a bit clearer where the supplementary material is now

# RT by optimal choice
plt1 <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ggplot(aes(RT, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt1$labels$x <- "Response Time (msecs)"
plt1$labels$fill <- "Optimal Choice"

plt1_5 <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ggplot(aes(log2_RT, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt1_5$labels$x <- "log2 transformed Response Time"
plt1_5$labels$fill <- "Optimal Choice"

@@

# what about RT by number of optimal choices
# only: - correct trials
#       - RT > 300ms
plt2 <- dat_ACS %>%
  na.omit() %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(RT),
            sum_optchoices = sum(Optimal_Choice)) %>%
  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
  geom_point() + 
  geom_text() + 
  theme_bw()
plt2$labels$x <- "No. of Optimal Choices"
plt2$labels$y <- "Mean RT (msecs)"

@@

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt3 <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc)) %>%
  mutate(mean_acc_ov = mean(mean_acc)) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt3$labels$x <- "Participant"
plt3$labels$y <- "Mean Accuracy"
# plt3

@@

```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
grid.arrange(plt1, plt1_5)
```

```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt2
```

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt3
```

@@

# mean RT by repetition rate? in each condition?
plt <- dat_for %>%
  na.omit() %>%
  mutate(sub_no = as.numeric(as.factor(sub_no))) %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, search_type, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, search_type) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = search_type)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt$labels$y <- "Response Time (secs)"
plt$labels$x <- "Average Repetition Rate"
plt$labels$colour <- "Search Condition"
plt

>>>>

# RT by optimal choice
plt_ACS_rt_opt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ggplot(aes(RT, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt_ACS_rt_opt$labels$x <- "Response Time (msecs)"
plt_ACS_rt_opt$labels$fill <- "Optimal Choice"

plt_ACS_logrt_opt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ggplot(aes(log2_RT, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt_ACS_logrt_opt$labels$x <- "log2 transformed Response Time"
plt_ACS_logrt_opt$labels$fill <- "Optimal Choice"

@@

# what about RT by number of optimal choices
# only: - correct trials
#       - RT > 300ms
plt_ACS_meanrt_opt <- dat_ACS %>%
  na.omit() %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(RT),
            sum_optchoices = sum(Optimal_Choice)) %>%
  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
  geom_point() + 
  geom_text() + 
  theme_bw()
plt_ACS_meanrt_opt$labels$x <- "No. of Optimal Choices"
plt_ACS_meanrt_opt$labels$y <- "Mean RT (msecs)"

@@

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt_ACS_mean_acc <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc)) %>%
  mutate(mean_acc_ov = mean(mean_acc)) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt_ACS_mean_acc$labels$x <- "Participant"
plt_ACS_mean_acc$labels$y <- "Mean Accuracy"
# plt3

@@

```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
```

```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_meanrt_opt
```

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```

@@

# mean RT by repetition rate? in each condition?
plt_for_sr_rt <- dat_for %>%
  na.omit() %>%
  mutate(sub_no = as.numeric(as.factor(sub_no))) %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, search_type, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, search_type) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = search_type)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt_for_sr_rt$labels$y <- "Response Time (secs)"
plt_for_sr_rt$labels$x <- "Average Repetition Rate"
plt_for_sr_rt$labels$colour <- "Search Condition"
plt_for_sr_rt
